Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-01-13 ForegroundSimulations/ms.tex
Add content under section 5.2
From 72bc820 (master):
=====================

In ms.tex,

(*) Add content under section 5.2

@@

\subsection{Constraints on Antenna-to-Antenna Reflections}

Patra~et~al.~2015 (submitted), Ewall-Wice~et~al.~2015 (submitted)

>>>>

Now we consider the effect of chromaticity of the power pattern on the delay power spectrum.

We simulate visibilities from our foreground model using three different models for the antenna power pattern -- {\it Airy} pattern, simulated dish, and a pattern at 150~MHz of the simulated dish assumed to be achromatic over the entire band.

Fig.~\ref{fig:asm-dps-beam-chromaticity} shows the delay power spectra of foregrounds obtained with the aforementioned models for power pattern. In all these panels, power spectra obtained with achromatic, {\it Airy} disk and simulated disk are shown in black, red, and blue respectively. The vertical gray lines denote the horizon limits for a 14.6~m antenna spacing. The full band delay power spectra of the foregrounds measured on a 14.6~m antenna spacing oriented eastward is shown in the top left panel. A clear trend of broadening of spillover-wings outside the horizon limits is seen with increasing chromaticity. For instance, the spillover from foreground delay power spectrum obtained with simulated dish pattern extends out to $k_\parallel \approx \pm 0.14\,h$~Mpc$^{-1}$, with the {\it Airy} pattern it extends out to $k_\parallel \approx \pm 0.08\,h$~Mpc$^{-1}$, while the achromatic beam extends it only out to $k_\parallel \approx \pm 0.05\,h$~Mpc$^{-1}$. Thus an increase in chromaticity extends the foreground spillover into higher $k_\parallel$-modes making them inaccessible for EoR H{\sc i} signal detection.

Following the foreground removal strategy, the top middle panel shows these foreground delay spectra deconvolved using the complex delay CLEAN algorithm \citep{tay99,par09,par12b}. The CLEAN window covers delay bins between the horizon delay limits and extends further by three delays bins on each side of the horizon limit where a delay bin is of size inverse of the bandwidth. The panel at the top right shows the residuals left behind after deconvolution.

@@

Owing to the chromaticity of power patterns, the spillover from foregrounds extends beyond the horizon limits, most severely in the simulated disk pattern. As a result the residuals have significant power remaining on either side of the horizon limits since the window for deconvolution is narrower than the extent of spillover along $k_\parallel$. The two peaks on either side is most severe for the simulated disk pattern followed by that for the {\it Airy} disk pattern and least for an achromatic power pattern.

We investigate the effect of chromaticity of power pattern in a foreground avoidance strategy that avoids the aforementioned deconvolution of delay spectrum. Application of window functions with high sidelobe suppression have been discussed for mitigating foreground contamination \citep{thy13}. In line with the foreground avoidance strategy, the visibilities from the full band foreground simulation (whose delay power spectrum is shown on the top left) are multiplied by a Blackman-Harris window function of 10~MHz effective bandwidth. The delay power spectra so produced are shown in the panel on the bottom left. Due to the decreased effective bandwidth the resolution of the delay power spectrum appears decreased. Hence, only the $|k_\parallel| \gtrsim 0.14\,h$~Mpc$^{-1}$ modes remain accessible. Due to the overall lower amplitude of the {\it Airy} power pattern relative to the simulated dish power pattern and the achromatic pattern, the sidelobe levels of foreground delay power spectra from an {\it Airy} pattern are lower than the other models by almost two orders of magnitude.

Following a delay-deconvolution based foreground removal strategy, we apply the Blackman-Harris window of effective bandwidth 10~MHz on the unsubtracted foreground residuals (top right panel) in frequency domain and obtain the delay power spectrum shown in the bottom right panel. It is noted that lesser the chromaticity the more effective the deconvolution process is in lowering the residuals in and around the horizon limits. For instance, the peak of the delay power spectrum using the achromatic beam is lowered by four orders of magnitude relative to the original peak whereas the residuals of delay power spectra with chromatic {\it Airy} and simulated power patterns is lowered only by two orders of magnitude. However, owing to the ineffective subtraction of the response extended beyond the horizon limits, the sidelobe levels have not been lowered significantly and are within an order of magnitude of each other.

In both strategies, the EoR H{\sc i} signal power spectrum obtained by simulations with 21cmFAST (Mesinger et al. 2008) is shown for reference (dashed black lines) in the bottom panels.

\subsection{Constraints on Reflections between Antennas}

Patra~et~al.~2015 (submitted) and Ewall-Wice~et~al.~2015 (submitted) discuss the measured and simulated reflections between a dish and its feed.
